\begin{zed}
[PROPID,LEGAJO,STRING] \\
N == \nat \\
msg ::= ok | error \\
ESTADOPROPIEDAD ::= venta | reservada | dadadebaja | vendida
\end{zed}

\begin{schema}{Inmobiliaria}
direcciones: PROPID \pfun STRING \\
titulos: PROPID \pfun STRING \\
precios: PROPID \pfun \nat \\
estados: PROPID \pfun ESTADOPROPIEDAD \\
gestores: PROPID \pfun LEGAJO \\
nombres: LEGAJO \pfun STRING \\
telefonos: LEGAJO \pfun STRING \\
emails: LEGAJO \pfun STRING
\end{schema}

\begin{schema}{InmobiliariaInicial}
Inmobiliaria
\where
direcciones = \emptyset  \\
titulos = \emptyset  \\
precios = \emptyset  \\
estados = \emptyset  \\
gestores = \emptyset  \\
nombres = \emptyset  \\
telefonos = \emptyset  \\
emails = \emptyset
\end{schema}

\begin{schema}{InmobiliariaInvariante}
Inmobiliaria
\where
\dom direcciones = \dom titulos \\
\dom titulos = \dom precios \\
\dom precios = \dom estados \\
\dom estados = \dom gestores \\
\dom nombres = \dom telefonos \\
\dom telefonos = \dom emails \\
\ran gestores \subseteq \dom nombres
\end{schema}

\begin{schema}{PropiedadExiste}
\Xi Inmobiliaria \\
propId?:PROPID \\
res!:msg
\where
propId? \in \dom direcciones \\
res! = error
\end{schema}

\begin{schema}{VendedorNoExiste}
\Xi Inmobiliaria \\
prod?:LEGAJO \\
res!:msg
\where
prod? \notin \dom nombres \\
res! = error
\end{schema}

\begin{schema}{InsertarPropiedadOk}
\Delta Inmobiliaria \\
propId?:PROPID \\
prod?:LEGAJO \\
dir?:STRING \\
tit?:STRING \\
p?:N \\
res!:msg
\where
prod? \in \dom nombres \\
propId? \notin \dom direcciones \\
direcciones =  direcciones \cup \{propId? \mapsto dir?\}  \\
titulos = titulos \cup \{propId? \mapsto tit?\}  \\
precios = precios \cup \{propId? \mapsto p?\}  \\
estados = estados \cup \{propId? \mapsto venta\}  \\
gestores = gestores \cup \{propId? \mapsto prod?\}  \\
nombres' =  nombres  \\
telefonos' =  telefonos  \\
emails' =  emails  \\
res! = ok
\end{schema}

\begin{zed}
InsertarPropiedad == InsertarPropiedadOk \lor VendedorNoExiste \lor PropiedadExiste
\end{zed}

\begin{schema}{VendedorExiste}
\Xi Inmobiliaria \\
propId?:LEGAJO \\
res!:msg
\where
propId? \in \dom nombres \\
res! = error
\end{schema}

\begin{schema}{InsertarVendedorOk}
\Delta Inmobiliaria \\
nom?:STRING \\
tel?:STRING \\
em?:STRING \\
prod?:LEGAJO \\
res!:msg
\where
prod? \notin \dom nombres \\
nombres' = nombres \cup \{prod? \mapsto nom?\}  \\
telefonos' = telefonos \cup \{prod? \mapsto tel?\}  \\
emails' =  emails \cup \{prod? \mapsto em?\}  \\
direcciones' = direcciones\\
titulos' = titulos\\
precios' = precios\\
estados' = estados\\
gestores' = gestores\\
res! = ok
\end{schema}

\begin{zed}
InsertarVendedor == InsertarVendedorOk \lor VendedorExiste
\end{zed}

\begin{schema}{PropiedadesGestionadasOk}
\Xi Inmobiliaria \\
prod?:LEGAJO \\
props!:\power PROPID
\where
prod? \in \dom nombres \\
props! = \dom(gestores \rres \{prod?\})
\end{schema}

\begin{zed}
PropiedadesGestionadas == PropiedadesGestionadasOk \lor VendedorNoExiste
\end{zed}